\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-07 related-work.tex
adjust claim about Coq a la carte

\citet{forsta2020} introduce \emph{Coq à la carte}.
It still follows DTC, but rather than embracing DTC's use of generic
fixed points, it considers specific instantiations instead.
The resulting mechanism appears more streamlined than prior \emph{à la
carte} approaches particularly for its extensive tool support for generating boilerplate code.
%
The approach does not seem to fully address the expression problem,
as \citet{liwei2022} observe, in that extending a composed
mechanization requires recompilation.

Our approach addresses the expression problem by extending the
linguistic facilities offered by a proof assistant.
Families, in particular, offer an organizational advantage.  They allow
grouping and coevolving related types, functions, and proofs without
explicit parameterization;
all further-bindable fields are automatically extensibility hooks.
Because family polymorphism does not require explicit parameterization
or complex encodings,
the resulting programming experience and code are accessible to the
working Coq programmer.
The more OO aspects of family polymorphism, such as the ability to
override and families as mixins, also facilitate extensibility and reuse
with minimal programmer effort.

>>>>

\citet{forsta2020} introduce \emph{Coq à la carte}.
It still follows DTC, but rather than embracing DTC's use of generic
fixed points, it considers specific instantiations instead.
The resulting mechanism appears more streamlined than prior \emph{à la
carte} approaches particularly for its extensive tool support for generating boilerplate code.
%
But even with the tool support, components of individually developed
feature extensions (e.g., "substlem") have to be composed separately by
invoking the tool.
%
%The approach does not seem to fully address the expression problem,
%as \citet{liwei2022} observe, in that further extending a composed
%mechanization causes (a small amount of) boilerplate code that glues definitions
%to be regenerated.

Our approach addresses the expression problem by extending the
linguistic facilities offered by a proof assistant.
Families, in particular, offer an organizational advantage.  They allow
grouping and coevolving related types, functions, and proofs without
explicit parameterization;
all further-bindable fields are automatically extensibility hooks.
Because family polymorphism does not require explicit parameterization
or complex encodings,
the resulting programming experience and code are accessible to the
working Coq programmer.
The more OO aspects of family polymorphism, such as the ability to
use families as mixins and the ability to grow a series of mechanized
languages in integral increments, also facilitate extensibility and
reuse
with minimal programmer effort.
